Dragonfly Territory Ananlysis

### 2020-12-01 analysis/analysisSS.Rmd
tweaking species numbers

@@

odonata_names <- read.csv("~/GitHub/rrirfinalproject/odonata_names.csv")

>>>>

# I want to know how many species there are in a given year, using the nrow function from base
# I will save each as with a corresponding year identifier because I have not yet decided what format I want them all in (dataframe, table, etc.)

ASpecies <- length(which(fullAbundanceDF[1,2:11] != 0))
BSpecies <- length(which(fullAbundanceDF[2,2:11] != 0))
CSpecies <- length(which(fullAbundanceDF[3,2:11] != 0))
DSpecies <- length(which(fullAbundanceDF[4,2:11] != 0))
ESpecies <- length(which(fullAbundanceDF[5,2:11] != 0))
FSpecies <- length(which(fullAbundanceDF[6,2:11] != 0))
GSpecies <- length(which(fullAbundanceDF[7,2:11] != 0))
HSpecies <- length(which(fullAbundanceDF[8,2:11] != 0))
ISpecies <- length(which(fullAbundanceDF[9,2:11] != 0))
JSpecies <- length(which(fullAbundanceDF[10,2:11] != 0))
KSpecies <- length(which(fullAbundanceDF[11,2:11] != 0))
LSpecies <- length(which(fullAbundanceDF[12,2:11] != 0))
MSpecies <- length(which(fullAbundanceDF[13,2:11] != 0))
NSpecies <- length(which(fullAbundanceDF[14,2:11] != 0))
OSpecies <- length(which(fullAbundanceDF[15,2:11] != 0))
PSpecies <- length(which(fullAbundanceDF[16,2:11] != 0))
QSpecies <- length(which(fullAbundanceDF[17,2:11] != 0))
RSpecies <- length(which(fullAbundanceDF[18,2:11] != 0))
SSpecies <- length(which(fullAbundanceDF[19,2:11] != 0))
TSpecies <- length(which(fullAbundanceDF[20,2:11] != 0))
USpecies <- length(which(fullAbundanceDF[21,2:11] != 0))
VSpecies <- length(which(fullAbundanceDF[22,2:11] != 0))
XSpecies <- length(which(fullAbundanceDF[23,2:11] != 0))
YSpecies <- length(which(fullAbundanceDF[24,2:11] != 0))
ZSpecies <- length(which(fullAbundanceDF[25,2:11] != 0))
AASpecies <- length(which(fullAbundanceDF[26,2:11] != 0))
ABSpecies <- length(which(fullAbundanceDF[27,2:11] != 0))
ACSpecies <- length(which(fullAbundanceDF[28,2:11] != 0))
ADSpecies <- length(which(fullAbundanceDF[29,2:11] != 0))
AESpecies <- length(which(fullAbundanceDF[30,2:11] != 0))

@@

odonata_names <- read.table("~/GitHub/rrirfinalproject/odonata_names.csv")
